Causal graph analysis of COVID-19 observational data in German districts reveals effects of mobility, awareness, and temperature

### 2021-03-01 manuscript/v4_medrxiv_revision/discussion.Rmd
add new folders for revision, test latexdiff

In addition, in alignment with other recent published studies, our results confirm evidence which associated a negative effect of temperature on new COVID-19 cases [@bannister-tyrrell_preliminary_2020;@demongeot_temperature_2020;@liu_impact_2020;@qi_covid-19_2020;@shi_impact_2020;@sobral_association_2020;@tosepu_correlation_2020;@Wang2020temperature;@wu_effects_2020]. It is however controversial to other scientific literature describing no effects [@briz-redon_spatio-temporal_2020;@iqbal_nexus_2020;@jahangiri_sensitivity_2020;@juni_impact_2020;@yao_no_2020] or even converse correlations [@auler_evidence_2020;@xie_association_2020]. The conflicting results might be explained by different climates and characteristics of the populations under study. While we are confident that our strict causal analysis resulted in effect estimates as undistorted as possible, there might be unconsidered bias in those other studies. Further research needs to be done to elucidate the biological characteristics of the novel virus SARS-CoV-2 regarding its ambient temperature survival and transmission. Finally, we found a positive causal effect of increment precipitation and a raise in COVID-19 cases, which supports previous observations [@sobral_association_2020].

>>>>

In addition, in alignment with other recent published studies, our results confirm evidence which associated a negative effect of temperature on new COVID-19 cases [@bannister-tyrrell_preliminary_2020;@demongeot_temperature_2020;@liu_impact_2020;@qi_covid-19_2020;@shi_impact_2020;@sobral_association_2020;@tosepu_correlation_2020;@Wang2020temperature;@wu_effects_2020]. It is however controversial to other scientific literature describing no effects [@briz-redon_spatio-temporal_2020;@iqbal_nexus_2020;@jahangiri_sensitivity_2020;@juni_impact_2020;@yao_no_2020] or even converse correlations [@auler_evidence_2020;@xie_association_2020]. The conflicting results might be explained by different climates and characteristics of the populations under study. While we are confident that our strict causal analysis resulted in effect estimates as undistorted as possible, there might be unconsidered bias in those other studies. Further research needs to be done to elucidate the biological characteristics of the novel virus SARS-CoV-2 regarding its ambient temperature survival and transmission. Finally, we found a positive causal effect of increased precipitation and a raise in COVID-19 cases, which supports previous observations [@sobral_association_2020].
